---
title: "exrecise 8 of ch-2"
output: html_document
---
a) Use the read.csv() function to read the data into R. Call the loaded data college. Make sure that you have the directory set to the correct location for the data.
```{r}
library(ISLR)
#college <- read.csv("http://www-bcf.usc.edu/~gareth/ISL/College.csv")
data(College)
```

b) Look at the data using the View() function. You should notice that the first column is just the name of each university. We don’t really want R to treat this as data. However, it may be handy to have these names for later. Try the following commands:


(c) i. Use the summary() function to produce a numerical summary of the variables in the data set.
```{r}
summary(College)
```
Use the pairs() function to produce a scatterplot matrix of the first ten columns or variables of the data. Recall that you can reference the first ten columns of a matrix A using A[,1:10].

```{r}
pairs(College[,1:10]) 

```
Use the plot() function to produce side-by-side boxplots of
Outstate versus Private.


```{r}
plot(College$Private, College$Outstate)
```
Create a new qualitative variable, called Elite, by binning
the Top10perc variable. We are going to divide universities
into two groups based on whether or not the proportion
of students coming from the top 10% of their high school
classes exceeds 50%.

```{r}
Elite <- rep("No", nrow(College))
Elite[College$Top10perc > 50] <- "Yes"
Elite <- as.factor(Elite)
College <- data.frame(College, Elite)
```
Use the summary() function to see how many elite universities there are. Now use the plot() function to produce side-by-side boxplots of Outstate versus Elite.

```{r}
summary(College)
# 78
plot(College$Elite, College$Outstate)
```
Use the hist() function to produce some histograms with differing numbers of bins for a few of the quantitative vari- ables. You may find the command par(mfrow=c(2,2)) useful: it will divide the print window into four regions so that four plots can be made simultaneously. Modifying the arguments to this function will divide the screen in other ways.

```{r}
par(mfrow=c(2,2))
hist(College$Top10perc, xlab = "Top 10%", main="")
hist(College$Top25perc, xlab = "Top 25%", main="")
hist(College$Grad.Rate, xlab = "Graduation rate", main="")
hist(College$PhD, xlab = "Proportion of faculty with Ph.D.’s", main="")
```
Proportion of Phd faculty in elite schools vs. not elite schools
```{r}
EliteSchools <- subset(College, College$Elite=="Yes")
NotEliteSchools <- subset(College, College$Elite=="No")
par(mfrow=c(1,2))
hist(EliteSchools$PhD)
hist(NotEliteSchools$PhD)
```

```{r}
par(mfrow=c(1,1))

eliteMean <- mean(EliteSchools$PhD)
eliteMean
notEliteMean <-mean(NotEliteSchools$PhD)
notEliteMean 
```

The mean proportion of faculty with Phd’s in the elite schools is 89.3205128
 and the mean proportion in non elite schools is 70.8011445
.