---
title: "exercise 10 of ch-3"
output: html_document
---
a) Fit a multiple regression model to predict Sales using Price,
Urban, and US.
```{r}
library("ISLR")
data("Carseats")
head(Carseats)
lm1<-lm(Sales~Price*Urban*US,data=Carseats)
summary(lm1)
```
```{r}
lm2<-lm(Sales~Price+Urban+US, data = Carseats)
summary(lm2)
```
```{r}
lm3<-lm(Sales~Price+Urban+US+Urban:US+Price:US+Price:Urban, data = Carseats)
summary(lm3)
```
```{r}
lm4<-lm(Sales~Price+Urban+US+Urban:US, data = Carseats)
summary(lm4)
#sales~Price+Us are significant.
```


b) Provide an interpretation of each coefficient in the model. Be careful—some of the variables in the model are qualitative!

When price increases by 1 dollar and other predictors are held constant, sales decrease by 54.459 unit sales. In otherwords, when price increases by 1 dollar, the number of carseats sold decrease by 54,459.

A store’s sale is not affected by whether or not it is in a Urban area.

A store in the US sales 1200 more carseats (in average) than a store that is abroad.



c) Write out the model in equation form, being careful to handle
the qualitative variables properly.

$$
Sales_i=\beta_0+\beta_1\times Price_i+\beta_2 \times US_i+\epsilon_i
$$



d) For which of the predictors can you reject the null hypothesis Ho : βj = 0?

The predictor ‘Urban’. Its p-value is not statistically significant with a value of 0.936.



e) On the basis of your response to the previous question, fit a
smaller model that only uses the predictors for which there is
evidence of association with the outcome.

```{r}
lm.fit<-lm(Sales~Price+US, data=Carseats)
summary(lm.fit)
```



f) How well do the models in (a) and (e) fit the data?

R squared and adjusted R squared suggest that the model is not fitting the data well but is still significantly better than only including the intercept.



g) Using the model from (e), obtain 95 % confidence intervals for the coefficient(s).
```{r}
confint(lm.fit)
```


h) Is there evidence of outliers or high leverage observations in the model from (e)? 

 Based on the Normal.q-q pot and the Residuals vs Leverage plot, there are no evidence of such points.

```{r}
{par(mfrow=c(2,2))
plot(lm.fit)}
```

