---
title: "exercise 12"
output: html_document
---
a)
Write a function, Power(), that prints out the result of raising 2
to the 3rd power. In other words, your function should compute
23 and print out the results.

```{r}
Power <- function() {
    2^3
}

Power()
```


b) Create a new function, Power2(), that allows you to pass any two numbers, “x” and “a”, and prints out the value of “x^a”.
```{r}
Power2 <- function(x, a) {
    x^a
}

Power2(3, 8)
```

c) Using the Power2() function that you just wrote, compute 103, 817, and 1313.

```{r}
Power2(10, 3)
Power2(8, 17)
Power2(131, 3)
```

d) Now create a new function, Power3(), that actually returns the result “x^a” as an R object, rather than simply printing it to the screen. That is, if you store the value “x^a” in an object called “result” within your function, then you can simply return() this result.

```{r}
Power3 <- function(x , a) {
    result <- x^a
    return(result)
}
```

e) Now using the Power3() function, create a plot of f(x)=x3. The x-axis should display a range of integers from 1 to 10, and the y-axis should display x2. Label the axes appropriately, and use an appropriate title for the figure. Consider displaying either teh x-axis, the y-axis, or both on the log-scale.

```{r}
x=seq(1:10)
plot(x, Power3(x, 2), log = "xy", xlab = "Log of x", ylab = "Log of x^2", main = "Log of x^2 vs Log of x")
```

f) Create a function, PlotPower(), that allows you to create a plot of “x” against “x^a” for a fixed “a” and for a range of values of “x”

```{r}
PlotPower <- function(x, a) {
    plot(x, Power3(x, a))
}

PlotPower(1:10, 3)

```

